\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-06-09 archive/RD design archived.Rmd
modified:   analysis/RD design analysis.Rmd 	new file:   analysis/RD-design-analysis.log 	new file:   analysis/RD-design-analysis.tex 	new file:   analysis/RD_Plot_1st_Order.pdf 	new file:   analysis/RD_Plot_2nd_Order.pdf 	new file:   analysis/RD_Plot_3rd_Order.pdf 	new file:   analysis/donut_robust.tex 	new file:   archive/RD design archived.Rmd 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	new

```{r}
# these are the packages that we need to import
library(haven)
library(rdd)
library(ggplot2)
library(dplyr)
library(rdrobust)
library(plm)
library(xtable)
library(pander) # this is for table showing
library(latex2exp) # this is to export it
setwd("E:/umich/RealEstateBrokerage-main")
# need to place data on the base directory
data <- read_dta("template.dta")
working_directory <-"E:/umich/RealEstateBrokerage"
```

@@

@@

# Export the third RD plot to its own PDF file
pdf("RD_Plot_3rd_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 3,
       title = "RD-plot 3rd order polynomial",
       x.label = "Nearest distance to Lianjia's stores",
       y.label = "Log of income in the community")
dev.off() # Close the PDF device
```

```{r}
bw_methods <- c("mserd", "cerrd")
kernel_list <- c("uniform", "triangular")
results_list <- list()
counter <- 1
for (bw_method in bw_methods) {
    for (kernel_in in kernel_list){
        result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances, 
                     c = 0.41,
                     p = 1, 
                     bwselect = bw_method, kernel = kernel_in)

        effective_obs <- sum(result$N_h)

        results_list[[counter]] <- data.frame(
        Method = bw_method,
        Kernel = kernel_in,
        Estimate = format(result$coef[1], digits = 3, scientific = FALSE),
        SE = format(result$se[1], digits = 3, scientific = FALSE),
        Z = format(result$z[1], digits = 3, scientific = FALSE),
        PValue = format(result$pv[1], digits = 3, scientific = FALSE),
        Bandwidth = format(result$bws[1], digits = 3, scientific = FALSE),
        EffectiveObs = effective_obs
    )
        counter <- counter + 1
    }
}
results <- do.call(rbind, results_list)
latex_code <- print(xtable(results, 
                           caption = "RD Estimates with Different Bandwidth Selection Methods and Kernels", 
                           label = "tab:rd_bandwidth_kernel_results"), 
                    include.rownames = FALSE, 
                    type = "latex",
                    print.results = FALSE)
write(latex_code, file = paste(working_directory , "result_tables/rdd_result_summary.tex", sep='/'))
print(results)
```

# checkings:

@@

## Donut Hole Test

@@

```{r}
perform_rd_analysis <- function(cutoff, donut_width, h, b) {
  # select the data that we need
  panel_data_donut <- panel_data[!(panel_data$nearest_store_distances >= (cutoff - donut_width) & 
                                   panel_data$nearest_store_distances <= (cutoff + donut_width)),]
  # run the rdrobust result
  result_donut <- rdrobust(y = panel_data_donut$ln_income, 
                           x = panel_data_donut$nearest_store_distances, 
                           c = cutoff,
                           p = 1, h = h, b = b)
  # return the coefficient and the p value
  conventional <- c("Conventional", result_donut$coef[1, 1], result_donut$se[1, 1], result_donut$pv[1, 1])
  bias_corrected <- c("Bias-Corrected", result_donut$coef[2, 1], result_donut$se[2, 1], result_donut$pv[2, 1])
  robust <- c("Robust", 
              format(result_donut$coef[3, 1], digits = 3, scientific = FALSE), 
              format(result_donut$se[3, 1], digits = 3, scientific = FALSE), 
              format(result_donut$pv[3, 1], digits = 3, scientific = FALSE))

  # combine the results
  result_table <- rbind(conventional, bias_corrected, robust)
  colnames(result_table) <- c("Method", "Coef", "SE", "p-value")
  return(result_table)
}

cutoff = 0.41
donut_widths <- c(0.01, 0.0125, 0.015, 0.0175, 0.02, 0.0225, 0.025)
results <- list()

for (donut in donut_widths) {
  result <- perform_rd_analysis(cutoff, donut, 0.066, 0.135)
  results[[paste0("donut_", donut)]] <- result
}

```{r}
perform_rd_analysis <- function(cutoff, donut_width, h, b) {
  # select the data that we need
  panel_data_donut <- panel_data[!(panel_data$nearest_store_distances >= (cutoff - donut_width) & 
                                   panel_data$nearest_store_distances <= (cutoff + donut_width)),]
  # run the rdrobust result
  result_donut <- rdrobust(y = panel_data_donut$ln_income, 
                           x = panel_data_donut$nearest_store_distances, 
                           c = cutoff, covs = panel_data_donut[, control_variables],
                           p = 1, h = h, b = b)
  # return the coefficient and the p value
  conventional <- c("Conventional", result_donut$coef[1, 1], result_donut$se[1, 1], result_donut$pv[1, 1])
  bias_corrected <- c("Bias-Corrected", result_donut$coef[2, 1], result_donut$se[2, 1], result_donut$pv[2, 1])
  robust <- c("Robust", 
              format(result_donut$coef[3, 1], digits = 3, scientific = FALSE), 
              format(result_donut$se[3, 1], digits = 3, scientific = FALSE), 
              format(result_donut$pv[3, 1], digits = 3, scientific = FALSE))

  # combine the results
  result_table <- rbind(conventional, bias_corrected, robust)
  colnames(result_table) <- c("Method", "Coef", "SE", "p-value")
  return(result_table)
}

cutoff = 0.41
donut_widths <- c(0.01, 0.0125, 0.015, 0.0175, 0.02, 0.0225, 0.025)
results_with_control <- list()

for (donut in donut_widths) {
  result <- perform_rd_analysis(cutoff, donut, 0.066, 0.135)
  results_with_control[[paste0("donut_", donut)]] <- result
}
```

```{r}
# with controls
combined_results_with_control <- do.call(rbind, lapply(names(results_with_control), function(donut) {
  result <- results_with_control[[donut]]
  robust_result <- result[result[, "Method"] == "Robust", ]
  data.frame(Donut_Width = donut, Method = robust_result[1], Coef = robust_result[2], SE = robust_result[3], p_value = robust_result[4])
}))
colnames(combined_results_with_control) <- c("Donut Width", "Method", "Coef", "SE", "p-value")

# without controls
combined_results <- do.call(rbind, lapply(names(results), function(donut) {
  result <- results[[donut]]
  robust_result <- result[result[, "Method"] == "Robust", ]
  data.frame(Donut_Width = donut, Method = robust_result[1], Coef = robust_result[2], SE = robust_result[3], p_value = robust_result[4])
}))
colnames(combined_results) <- c("Donut Width", "Method", "Coef", "SE", "p-value")

merged_results <- merge(combined_results_with_control, combined_results, by = c("Donut Width", "Method"))
merged_results_df <- as.data.frame(merged_results)

colnames(merged_results_df) <- c("Donut Width", "Method", "Coef", "SE", "p-value", "Coef", "SE", "p-value")

# print as a latex table
latex_code <- print(xtable(merged_results_df, 
                           caption = "RD Analysis Donut RD Results with and without Controls", 
                           label = "tab:rd_robust_results"), 
                    include.rownames = FALSE, 
                    type = "latex",
                    print.results = FALSE)

latex_code <- gsub("\\\\begin\\{tabular\\}\\{llllllll\\}\n  \\\\hline\n", 
                   "\\\\begin{tabular}{llllllll}\n  \\\\hline\n &  & \\\\multicolumn{3}{c}{Without Control} & \\\\multicolumn{3}{c}{With Control} \\\\\\\\\n", 
                   latex_code)

latex_code <- gsub("\\\\end\\{tabular\\}", "\\\\end{tabular}\nNote that the cutoff is 0.41, the main bandwidth is 0.066 and the bias bandwidth is 0.135.", latex_code)

write(latex_code, file = paste(working_directory , "result_tables/donut_robust.tex", sep='/'))
```

## McCrary Sorting Test

```{r}
# Give it the running variable and the cutpoint
# it will automatically produce a plot and select the number of bins and the bandwidth
# The output will be the p-value for the presence of a discontinuity
DCdensity(filtered_data$nearest_store_distances, cutpoint = 0.41, bw = 0.066, verbose = TRUE, plot = FALSE)
DCdensity(panel_data$nearest_store_distances, cutpoint = 0.41, bw = 0.066, verbose = TRUE, plot = FALSE)
```

## PlaceBo Test

@@

```{r}
testing_variables <- c("pop", "light", "price_concession", "ln_end_price", "ln_nego_changes", "ln_watch_time", "green_ratio", "bedroom", "ln_watch_people", "living_room", "ln_negotiation_period", "museum", "kind", "mid", "sub", "house_age", "total_building")

@@

counter <- 1

for (validation in testing_variables) {
  rd_result <- rdrobust(y = panel_data[[validation]], x = panel_data$nearest_store_distances,
                        c = 0.41, h = 0.066, b = 0.135,
                        bwselect = "mserd", kernel = "triangular")

  # 提取有效观测值数量并相加
  effective_obs <- sum(rd_result$N_h)

  # 提取结果并存储到列表中
  results_list[[counter]] <- data.frame(
    Covariate = validation,
    Estimate = format(rd_result$coef[1], digits = 3, scientific = FALSE),
    SE = format(rd_result$se[1], digits = 3, scientific = FALSE),
    Z = format(rd_result$z[1], digits = 3, scientific = FALSE),
    PValue = format(rd_result$pv[1], digits = 3, scientific = FALSE),
    Bandwidth = format(rd_result$bws[1], digits = 3, scientific = FALSE),
    EffectiveObs = effective_obs
  )
  counter <- counter + 1
}

results <- do.call(rbind, results_list)

latex_code <- print(xtable(results, 
                           caption = "Placebo Test Results for Different Covariates", 
                           label = "tab:placebo_test_results"), 
                    include.rownames = FALSE, 
                    type = "latex",
                    print.results = FALSE)
write(latex_code, file = paste(working_directory , "result_tables/rdd_placebo_test.tex", sep='/'))
print(results)

## Cutoff Point movement

The movement of the cutoff point should make the estimation non-significant

```{r}
cutoffs_width <- c(0.15, 0.2, 0.25, 0.30, 0.35, 0.50, 0.65, 0.7)

results_list <- list()
counter <- 1
for (cutoff in cutoffs_width) {
  # rd_result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances, c = cutoff, h = 0.066, b = 0.135, bwselect = "mserd", kernel = "triangular")
  rd_result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances,
                        c = cutoff)

  # 提取有效观测值数量并相加
  effective_obs <- sum(rd_result$N_h)
  # 提取结果并存储到列表中
  results_list[[counter]] <- data.frame(
    Cutoff = cutoff,
    Estimate = format(rd_result$coef[1], digits = 3, scientific = FALSE),
    SE = format(rd_result$se[1], digits = 3, scientific = FALSE),
    Z = format(rd_result$z[1], digits = 3, scientific = FALSE),
    PValue = format(rd_result$pv[1], digits = 3, scientific = FALSE),
    Bandwidth = format(rd_result$bws[1], digits = 3, scientific = FALSE),
    EffectiveObs = effective_obs
  )
  counter <- counter + 1
}
results <- do.call(rbind, results_list)

latex_code <- print(xtable(results, 
                           caption = "Placebo Test Results for Different Cutoff Point", 
                           label = "tab:movement_cutoff"), 
                    include.rownames = FALSE, 
                    type = "latex",
                    print.results = FALSE)
write(latex_code, file = paste(working_directory , "result_tables/movement_cutoff.tex", sep='/'))
print(results)
```

>>>>

```{r}
# these are the packages that we need to import
library(haven)
library(ggplot2)
library(dplyr)
library(rdrobust)
library(plm)
library(pander) # this is for table showing
library(latex2exp) # this is to export it
setwd("E:/umich/RealEstateBrokerage-main")
# need to place data on the base directory
data <- read_dta("template.dta")
```

@@

```{r}
result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances, 
                   c = 0.41, covs = panel_data[, control_variables],
                   p = 1) # first using default clustering
```

@@

# Export the third RD plot to its own PDF file
pdf("RD_Plot_3rd_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 3,
       title = "RD-plot 3rd order polynomial",
       x.label = "Nearest distance to Lianjia's stores",
       y.label = "Log of income in the community")
dev.off() # Close the PDF device

```{r}
result
```

```{r}
pander(cbind(result$coef, result$pv))
```

```{r}
result <- rdrobust(y = panel_data$pop, x = panel_data$nearest_store_distances, 
                   c = 0.41,
                   p = 1) # first using default clustering
result2 <- rdrobust(y = panel_data$light, x = panel_data$nearest_store_distances, 
                   c = 0.41,
                   p = 1)
result3 <- rdrobust(y = panel_data$ln_end_price, x = panel_data$nearest_store_distances, 
                   c = 0.41,
                   p = 1)
```

```{r}
pander(cbind(result$coef, result$pv))
pander(cbind(result2$coef, result2$pv))
pander(cbind(result3$coef, result3$pv))
```

note that the figure only shows points that are within the bandwidth, the whole points are shown in Appendix of the paper.

```{r}
h = 0.124
cutoff = 0.41
running_var = panel_data$nearest_store_distances

par(mfrow=c(3,1))
rdplot(y = filtered_data$ln_lead, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 1,
       title = "RD-plot",
       x.label = "nearest distance to lianjia's stores",
       y.label = "lianjia's income in the community")

rdplot(y = filtered_data$ln_lead, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 2,
       title = "RD-plot",
       x.label = "nearest distance to lianjia's stores",
       y.label = "lianjia's income in the community")

rdplot(y = filtered_data$ln_lead, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 3,
       title = "RD-plot",
       x.label = "nearest distance to lianjia's stores",
       y.label = "lianjia's income in the community")
```

```{r}
h = 0.158
cutoff = 0.41
running_var = panel_data$nearest_store_distances

par(mfrow=c(3,1))
rdplot(y = filtered_data$price_concession, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 1,
       title = "RD-plot",
       x.label = "nearest distance to lianjia's stores",
       y.label = "lianjia's income in the community")

rdplot(y = filtered_data$price_concession, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 2,
       title = "RD-plot",
       x.label = "nearest distance to lianjia's stores",
       y.label = "lianjia's income in the community")

rdplot(y = filtered_data$price_concession, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 3,
       title = "RD-plot",
       x.label = "nearest distance to lianjia's stores",
       y.label = "lianjia's income in the community")
```

checkings:

@@

@@

```{r}
donut_width <- 0.015
panel_data_donut <- panel_data[!(panel_data$nearest_store_distances >= (cutoff - donut_width) & 
                                 panel_data$nearest_store_distances <= (cutoff + donut_width)),]
result_donut <- rdrobust(y = panel_data_donut$ln_income, 
                         x = panel_data_donut$nearest_store_distances, 
                         c = cutoff,  covs = panel_data_donut[, control_variables],
                        p = 1, h = 0.095, b = 0.185)
pander(cbind(result_donut$coef, result_donut$pv))
print(result_donut)
```

```{r}

library(rdd)

# Give it the running variable and the cutpoint
# it will automatically produce a plot and select the number of bins and the bandwidth
# The output will be the p-value for the presence of a discontinuity
DCdensity(panel_data$nearest_store_distances, cutpoint = 0.41, bw = 0.066, verbose = TRUE, plot = FALSE)
```

```{r}
library(rdd)

# Give it the running variable and the cutpoint
# it will automatically produce a plot and select the number of bins and the bandwidth
# The output will be the p-value for the presence of a discontinuity
DCdensity(panel_data$nearest_store_distances, cutpoint = 0.41, bw = 0.095, verbose = TRUE, plot = FALSE)
```

@@

```{r}
for (validation in testing_variables) {
  rd_result <- rdrobust(y = panel_data[[validation]], x = panel_data$nearest_store_distances
                        , c = 0.41, h = 0.066, b = 0.135)
  cat("Covariate:", validation, "\n")
  print(summary(rd_result))
  cat("\n\n")

}
```

```{r}
results <- data.frame(
  Cutpoint = numeric(),
  Bandwidth = numeric(),
  LogDiff = numeric(),
  SE = numeric(),
  ZStat = numeric(),
  PValue = numeric()
)

h = 0.066
cutoff = 0.41
running_var = panel_data$nearest_store_distances

# 定义切点和带宽的向量
cutpoints <- c(0.41)
bandwidths <- c(0.60, 0.063, 0.066, 0.069, 0.72)

@@

# 循环遍历切点和带宽
counter <- 1
for (cutpoint in cutpoints) {
  for (bw in bandwidths) {
    # 运行 McCrary Sorting Test 并捕获输出
    capture_output <- capture.output(result <- DCdensity(filtered_data$nearest_store_distances, cutpoint = cutpoint, bw = bw, verbose = TRUE, plot = FALSE))

    # 提取结果
    log_diff <- as.numeric(sub(".*Log difference in heights is\\s+([-+]?\\d*\\.\\d+).*", "\\1", capture_output[grep("Log difference in heights is", capture_output)]))
    se <- as.numeric(sub(".*with SE\\s+([-+]?\\d*\\.\\d+).*", "\\1", capture_output[grep("with SE", capture_output)]))
    z_stat <- as.numeric(sub(".*this gives a z-stat of\\s+([-+]?\\d*\\.\\d+).*", "\\1", capture_output[grep("this gives a z-stat of", capture_output)]))
    p_value <- as.numeric(sub(".*and a p value of\\s+([-+]?\\d*\\.\\d+).*", "\\1", capture_output[grep("and a p value of", capture_output)]))

    # 将结果存储到列表中
    results_list[[counter]] <- data.frame(
      Cutpoint = cutpoint,
      Bandwidth = bw,
      LogDiff = log_diff,
      SE = se,
      ZStat = z_stat,
      PValue = p_value
    )
    counter <- counter + 1
  }
}

# 将结果列表转换为数据框
results <- do.call(rbind, results_list)

# 打印结果数据框
print(results)
```

### 2024-06-09 manuscript/main.tex
modified:   analysis/RD design analysis.Rmd 	new file:   analysis/RD-design-analysis.log 	new file:   analysis/RD-design-analysis.tex 	new file:   analysis/RD_Plot_1st_Order.pdf 	new file:   analysis/RD_Plot_2nd_Order.pdf 	new file:   analysis/RD_Plot_3rd_Order.pdf 	new file:   analysis/donut_robust.tex 	new file:   archive/RD design archived.Rmd 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	new

The second hand housing transaction data was collected form \href{https://bj.lianjia.com/}{lianjia.com} for ten cities ranging from 2016 to 2022. Initially, we filtered out transaction records exhibiting unusually high prices, identifying them as outliers that could skew the analysis. We then removed records with missing values to maintain the integrity of our dataset. We also removed any records that were listed duplicated. We finally have a data with length 1,716,579 second-hand house.\footnote{Due to government restrictions, four of these cities did not list the transaction price for each transaction during the study period.} Since most of the offline stores in lianjia are community-based, and most of the information is accurate at the community level, we decided to aggregate the information at the community level to make our panel compatible. By taking the average of all transaction information, we constructed the panel data with seven years.

@@

From Figure \ref{fig:RD_design} we can see that there is indeed discontinuity in 410 meters of communities to the nearest Lianjia's store, which is pretty close to the lianjia's 5-minute walk distance policy. The observed decline in the Lianjia's influence is marked and suggests a pronounced reduction in its impact on the system overall within our study sample. This phenomenon can be attributed to the implementation of the Lianjia's proximity to customers policy, which is evidenced at the data level.

To make the robust check we conducted Donut Hole test by excluding observations close to the cutoff and estimating the effect with the remaining data. The results are shown in Appendix and the result shows that the discontinuity still exists and this provides evidence against a model misspecification. Furthermore, we carry out the density test by \citep{MCCRARY2008698}. The result shows that the p-value is greater than 0.1, which suggests the result is not due to manipulation of polygons. Finally, we carry out placebo tests which are reported in Appendix, which strengthens the case for a true treatment effect.

@@

>>>>

The second hand housing transaction data was collected form \href{https://www.ke.com/city/}{beke.com} for ten cities ranging from 2016 to 2022. Initially, we filtered out transaction records exhibiting unusually high prices, identifying them as outliers that could skew the analysis. We then removed records with missing values to maintain the integrity of our dataset. We also removed any records that were listed duplicated. We finally have a data with length 1,716,579 second-hand house.\footnote{Due to government restrictions, four of these cities did not list the transaction price for each transaction during the study period.} Since most of the offline stores in lianjia are community-based, and most of the information is accurate at the community level, we decided to aggregate the information at the community level to make our panel compatible. By taking the average of all transaction information, we constructed the panel data with seven years.

@@

\input{../result_tables/rdd_result_summary.tex}

From Figure \ref{fig:RD_design} we can see that there is indeed discontinuity in 410 meters of communities to the nearest Lianjia's store, which is pretty close to the lianjia's 5-minute walk distance policy. The observed decline in the Lianjia's influence is marked and suggests a pronounced reduction in its impact on the system overall within our study sample. This phenomenon can be attributed to the implementation of the Lianjia's proximity to customers policy, which is evidenced at the data level. Table \ref{tab:rd_bandwidth_kernel_results} considers different kernel and bandwidth choices, and the results are consistent with the 410 meters radius. The only non-significance is the CER-optimal bandwidth selector with triangular kernel, which is because the selected bandwidth is too small to capture the discontinuity. The results are robust to different bandwidth and kernel choices, which suggests that the 410 meters is the optimal radius for Lianjia's offline stores.

To make the robust check we conducted Donut Hole test by excluding observations close to the cutoff and estimating the effect with the remaining data. The results are shown in Appendix and the result shows that the discontinuity still exists and this provides evidence against a model misspecification. Furthermore, we carry out the density test by \citep{MCCRARY2008698}. The result shows that the p-value is greater than 0.1 (p value equals 0.101), which suggests the result is not due to manipulation of polygons. Finally, we carry out placebo tests which are reported in Appendix, which shows that our result is robust. Specifically, Table \ref{tab:placebo_test_results} shows that the discontinuity does not exist in the placebo test, which suggests that our result is not due to the manipulation of the data. Table \ref{tab:movement_cutoff} shows that other cutoffs do not have the same effect as the 410 meters cutoff, which suggests that the 410 meters is the optimal radius for Lianjia's offline stores.

@@

\input{../result_tables/donut_robust.tex}

\input{../result_tables/rdd_placebo_test.tex}

\input{../result_tables/movement_cutoff.tex}
